---
title: "Data Structures in R"
author: "Maybin Katongo"
date: "8/23/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Data Structures in R

This Document explains in summary some of the data structures in R programining.

## Atomic Vectors
* An atomic vector is just a simple vector in R
```{r }
die <- c(1, 2, 3, 4, 5, 6)
die
# Check if data structures
is.vector(die)
typeof(die)
```

## Integers
Integers are numbers that can be written without a decimal component
You create integers values by put L in front of a number

```{r}
int <- 1L
print(int)
# Check type of data type
typeof(int)

```

## Doubles
Double are numbers in R with digits to the right of the decimal or not and can either be positive of negative. R will save any number the you type in R as double


```{r}
die <- c(1, 2, 3, 4, 5, 6)
print(die)
# Check type of data type
typeof(die)

```


## Characters
A character vector stores small pieces of text

```{r}
text <- c("Hello", "World")
print(text)
# Check type of data type
typeof(text)

```


## Logicals
Logical vector store TRUEs and FALSEs, R's form of Boolean data.
Helpful for doing comparisons

```{r}
logic <- c(TRUE, FALSE, TRUE)
print(logic)
# Check type of data type
typeof(logic)
````